---
title: "HW5"
author: "Peter Ciliberto"
output: html_document
---

## Problem 0 

https://github.com/peterciliberto/HW5.git

# Part 1

## Problem 1 

```{r}
rankcor <-function(x, y){
  n <-length(x)
  stopifnot(length(y)==n)
  
  x.ranks <-rank(x)
  y.ranks <-rank(y)
  
  mean.x <-mean(x.ranks)
  mean.y <-mean(y.ranks)
  
  covariance.term <-cov(x.ranks-mean.x, y-mean.y)
  
  sd.x <-sd(x.ranks)
  sd.y <-sd(y.ranks)
  
  rank.cor <- covariance.term/(sd.x*sd.y)
  
  return(rank.cor)}
```

The first line of the function sets n to the legnth of x
The second line ensures that the funciton will not run if the length of y does not equal n, which is the length of x
The third and fourth lines gives a rank to the x and y values based on the rank correlation.
The fifth and sixth lines compute the mean of the ranked x and y values.
The seventh line computes the covariance between x and y 
The eigth and ninth lines compute the standard deviation of x and y 
The tenth line computes the rank correlation.

## Problem 2

```{r}
x <- c(2,4,6,8)
y <- c(64,36,16,4)
rankcor <-function(x, y){
  n <-length(x)
  stopifnot(length(y)==n)
  
  x.ranks <-rank(x)
  y.ranks <-rank(y)
  
  mean.x <-mean(x.ranks)
  mean.y <-mean(y.ranks)
  
  covariance.term <-cov(x.ranks-mean.x, y-mean.y)
  
  sd.x <-sd(x.ranks)
  sd.y <-sd(y.ranks)
  
  rank.cor <- covariance.term/(sd.x*sd.y)
  
  return(rank.cor)}
rankcor(x,y)
```

The value that we get for the rank correlation is -20

## Problem 3 

This answer must be wrong because the rank correlation only varies from -1 to 1

## Problem 4 
 
```{r}
x <- c(1,2,3,4)
y <- c(4,3,2,1)

rankcor <-function(x, y){
  n <-length(x)
  stopifnot(length(y)==n)
  
  x.ranks <-rank(x)
  y.ranks <-rank(y)
  
  mean.x <-mean(x.ranks)
  mean.y <-mean(y.ranks)
  
  covariance.term <-cov(x.ranks-mean.x, y-mean.y)
  
  sd.x <-sd(x.ranks)
  sd.y <-sd(y.ranks)
  
  rank.cor <- covariance.term/(sd.x*sd.y)
  
  return(rank.cor)}
rankcor(x,y)
```

I know this answer is correct because the vector x and vector y that I chose have a perfect negative linear relationship. 

# Part 2

## Problem 5 

```{r}
test.rankcor <- function(fun = rankor){
  
}
```

## Problem 6 

The bug in the function occurs in the seventh line of the code where the covariance is computed. The code reads:

covariance.term <-cov(x.ranks-mean.x, y-mean.y) 

where it should read:

covariance.term <-cov(x.ranks-mean.x, y.ranks-mean.y)

This bug is the result of using the vector y instead of y.ranks to calculate the covariance.

## Problem 7 

```{r}
x <- c(2,4,6,8)
y <- c(64,36,16,4)
rankcor <-function(x, y){
  n <-length(x)
  stopifnot(length(y)==n)
  
  x.ranks <-rank(x)
  y.ranks <-rank(y)
  
  mean.x <-mean(x.ranks)
  mean.y <-mean(y.ranks)
  
  covariance.term <-cov(x.ranks-mean.x, y.ranks-mean.y)
  
  sd.x <-sd(x.ranks)
  sd.y <-sd(y.ranks)
  
  rank.cor <- covariance.term/(sd.x*sd.y)
  
  return(rank.cor)}
rankcor(x,y)
```

## Problem 8 

The average rank of a vector is always n/2 + 1/2 because the rank() function assigns a rank to each value in a vector a rank from 1:n. The average rank of a vector is then the mean of the ranks.

```{r}
x <- c(2,4,6,8)
y <- c(64,36,16,4)
rankcor <-function(x, y){
  n <-length(x)
  stopifnot(length(y)==n)
  
  x.ranks <-rank(x)
  y.ranks <-rank(y)
  
  mean <- n/2 + 1/2
  
  covariance.term <-cov(x.ranks-mean, y.ranks-mean)
  
  sd.x <-sd(x.ranks)
  sd.y <-sd(y.ranks)
  
  rank.cor <- covariance.term/(sd.x*sd.y)
  
  return(rank.cor)}
rankcor(x,y)
```

## Problem 9 

It is unnecessary to subtract off the mean rank while using cov() because the mean rank for x and y will always be the same in this function. 

```{r}
x <- c(2,4,6,8)
y <- c(64,36,16,4)
rankcor <-function(x, y){
  n <-length(x)
  stopifnot(length(y)==n)
  
  x.ranks <-rank(x)
  y.ranks <-rank(y)
  
  covariance.term <-cov(x.ranks, y.ranks)
  
  sd.x <-sd(x.ranks)
  sd.y <-sd(y.ranks)
  
  rank.cor <- covariance.term/(sd.x*sd.y)
  
  return(rank.cor)}
rankcor(x,y)
```

## Problem 10

```{r}

```




































































































